Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-03-24 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/paper.tex
Some part of the introduction was written down.

>>>>

There is a branch in the theory for the formal languages which is related to a context-free grammar (CFG). In such grammar there are set of production rules. Application of these rules lead to generation of all possible strings in a specified formal language. In CFG a production rule is an operation of simple replacement. Rules are applied regardless of the context. The left hand side of a CFG rule is always nonterminal symbol. It means that nonterminal symbols are not part of the resulting string. The right hand side of a CFG rule consists of terminal symbol, nonterminal symbols or combination of both. The main idea in CFGs is that nonterminal symbols are substituted with the given rules until there is no nonterminal symbols in the generated string.

String rewriting system (SRS) is a substitution system in which rules does not contain nonterminal symbols. Each terminal symbol can appear on the LHS of the rule and on the RHS of the rule. With such definition SRS are useful for generation of infinite structures and they are mainly used for the generation of some fractals (for example: Box Fractal, Cantor Dust, Cantor Square Fractal and Sierpinski Carpet). Most of the fractals are generated with binary rules (black and white colors), but in the Hodkinson's research it is clearly shown that limit of the colors can be higher.

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\linewidth]{pic01}
  \caption{Fractal generated by Jack Hodkinson.}
\label{fig:pic01}
\end{figure}

In Hodkinson's research genetic algorithms (GAs) were employed in order 2D shape of Greek letter $\pi$ to be reconstructed with substitution rules of 30 shades of blue pixels (Fig. \ref{fig:pic01}). The key problem in his research was wich 30 rules to be selected in order the final goal to be achieved. GAs were a promising approach for such kind of combinatorial optimization. A single rule had LHS pixel with particular color and nine pixels on the RHS as 3x3 substitution matrix. Image starts with a single pixel and it grows on size by 3 on each generation.
